\section{Objective}
\large
\subsection{Develop a Novel Detection Method:}
Design and implement the Bi-granularity artifacts (BiG-Arts) approach, which focuses on detecting intrinsic and extrinsic artifacts left by DeepFake generation processes.
Utilize multi-task learning to predict both types of artifacts simultaneously, enhancing the detection accuracy.
Enhance Detection Accuracy:
\subsection{Improve the detection accuracy of DeepFake videos}
 In both within-dataset and cross-dataset scenarios by leveraging the unique characteristics of bi-granularity artifacts.
Conduct extensive experiments on various DeepFake datasets to validate the effectiveness of the proposed method.
Benchmark Against Existing Methods:
\subsection{Compare the performance of the BiG-Arts approach with existing DeepFake detection methods}
Highlighting its advantages and areas for further improvement.
Aim to achieve top performance metrics in widely recognized benchmarks, such as the DeepFake Detection Challenge (DFGC).
Address Practical Challenges:
\subsection{Tackle the practical challenges associated with DeepFake detection}
Including the continuous evolution of face forgery techniques and the performance drop across different datasets.
Investigate methods to generalize the detection model, making it robust against various types of DeepFake videos and different levels of video quality.
Contribute to Societal Security:
\subsection{Provide a reliable and effective tool for identifying DeepFake videos}
Contributing to the broader efforts in maintaining societal security and trustworthiness.
Collaborate with stakeholders, including law enforcement agencies, media organizations, and social media platforms, to integrate the developed method into real-world applications for combating the misuse of DeepFakes.
Open Research Directions:
\subsection{Identify and explore new research directions based on the findings and limitations of the BiG-Arts approach.}

Encourage the research community to further investigate and improve DeepFake detection techniques, fostering ongoing advancements in this critical field.