
\section{References}

\begin{enumerate}
    \item J. Thies, M. Zollhofer, M. Stamminger, C. Theobalt, M. Nießner, \textit{Face2Face: real-time face capture and reenactment of RGB videos}, in: Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition, 2016, pp. 2387–2395.
    
    \item D. Afchar, V. Nozick, J. Yamagishi, I. Echizen, \textit{MesoNet: a compact facial video forgery detection network}, in: 2018 IEEE International Workshop on Information Forensics and Security (WIFS), 2018, pp. 1–7, doi:10.1109/WIFS.2018.8630761.
    
    \item A. Rossler, D. Cozzolino, L. Verdoliva, C. Riess, J. Thies, M. Nießner, \textit{FaceForensics++: learning to detect manipulated facial images}, in: Proceedings of the IEEE/CVF International Conference on Computer Vision, 2019, pp. 1–11.
    
    \item F. Chollet, \textit{Xception: deep learning with depthwise separable convolutions}, in: Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition, 2017, pp. 1251–1258.
    
    \item Y. Li, S. Lyu, \textit{Exposing DeepFake videos by detecting face warping artifacts}, in: IEEE Conference on Computer Vision and Pattern Recognition Workshops (CVPRW), 2019.
    
    \item H.H. Nguyen, J. Yamagishi, I. Echizen, \textit{Capsule-forensics: using capsule networks to detect forged images and videos}, in: ICASSP 2019 - 2019 IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP), 2019, pp. 2307–2311, doi:10.1109/ICASSP.2019.8682602.
    
    \item H. He, E.A. Garcia, \textit{Learning from imbalanced data}, IEEE Trans. Knowl. Data Eng. 21 (9) (2009) 1263–1284.
    
    \item D. Güera, E.J. Delp, \textit{DeepFake video detection using recurrent neural networks}, in: 2018 15th IEEE International Conference on Advanced Video and Signal Based Surveillance (AVSS), 2018, pp. 1–6, doi:10.1109/AVSS.2018.8639163.
    
    \item X. Li, Y. Lang, Y. Chen, X. Mao, Y. He, S. Wang, H. Xue, Q. Lu, \textit{Sharp multiple instance learning for DeepFake video detection}, in: Proceedings of the 28th ACM International Conference on Multimedia, 2020, pp. 1864–1872.
\end{enumerate}


